Points Above Replacement: A New NBA Metric to Evaluate Player Performance

### 2022-03-29 Manuscript/Manuscript.tex
Add files via upload

\usepackage{amsmath, enumerate, quoting, amssymb, subfigure, url}

@@

\usepackage{xr}
\externaldocument{isgee}
\externaldocument{supp}

@@

@@

% Abstracts are required.
\section*{abstract}
In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above Replacement, or WAR, to tell how many wins a 
team would gain or lose if they replaced a certain player with one who is league average. The goal of this paper is to create a similar statistic, called Points Above Replacement, or PAR, that uses statistics from throughout the season to predict how many points a 
team gains or loses by missing a certain player, and thus having to replace him with one who is "league average". The statistic is standardized and adjusted by both position and value to a player's given team. The model roughly follows the calculation of WAR in 
baseball, assigning values to points created on offense and defense, as well as a positional and team adjustment. A comparison with the created metric along with other well-known advanced player metrics is done via a multiple regression.

% Keywords are required.
\section*{keywords} 
NBA; Basketball; Player Performance; Basketball Metrics;
\vspace{.12 in}
% Start the main part of the manuscript here.
% Comment out section headings if inappropriate to your discipline.
% If you add additional section or subsection headings, use an asterisk * to avoid numbering.

@@

\section{Data}
% Include basic graphics here?
All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference website. Each teams total points throughout the course of the season were also collected from the Basketball Reference website.

From the basic statistics, 4 metrics were created in order to calculate PAR. Offensive Points is a function of how many points a player will create on offense. While the coefficients vary by position, the statistics used are effective field goal percentage, three point 
percentage, free throw percentage, offensive rebounds, assists, points, and turnovers. Similarly, Defensive Points is a function of how many points a player helps prevent while his team is on defense. The coefficients also vary by position, but this metric is based 
on defensive rebounds, total rebounds, steals, blocks, and personal fouls. The Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is based on how many minutes a player plays relative to their team, as well 
as how many points they score relative to their teams total points. The last statistic created is Points Per Win, which is based on the average amount of points a player will create in a game. This function is based on the sum of Offensive and Defensive Points, 
and is scaled to incorporate the total number of games, minutes, and players in a season. This statistic is very similarly calculated to Runs Per Win in the WAR statistic.

Given that over the course of a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in terms of strength of schedule. Advanced statistics for each player were also collected in order to perform a regression, to 
see how PAR compares with known and accepted metrics. Value Over Replacement Player, also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus Minus, also known as BPM. These statistics also help give a 
relative estimate of a player's value compared to that of an average player, but they translate the statistic to a league average team as well. PAR does not do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire 
league. If a player switched teams, his PAR value would most likely change, as his importance to one team may be more or less than it would to another. For simplicity, the team that a player played his most games on was taken into consideration for this metric. 
Other statistics used include Player Efficiency Rating, a per-minute rating of player performance, and Win Shares, which estimates the number of wins a player creates for his team throughout the season. Due to all of these metrics' relative similarity to PAR, it is 
suggested that if they are highly correlated with PAR, it is a successful metric. However, we expect some differentiation between the metrics, as they all vary slightly in what they attempt to convey. The relative correlation between all these statistics shows that 
PAR is related to other advanced metrics analyzing player efficiency, but also that it introduces something new in basketball statistics.

@@

\section{Results}
% Multiple Regression
% Analyze Graphs of PAR, filter by position perhaps?
% Any other tests that should be done?
First, the top 10 players in terms of PAR in the league will be analyzed. Then, the top 10 PAR values at each position will be evaluated.
\begin{NBAtable}[tbp]
  \caption{PAR Values from the Entire NBA)
  \label{tab:NBAtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Position & Team & PAR\\
  \midrule
 1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
  \midrule
 3 & Julius Randle & PF & New York Knicks & 6.49\\
  \midrule
 4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
  \midrule
 5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
  \midrule
 6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
  \midrule
 7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
  \midrule
 8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
  \midrule
 9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
  \midrule
 10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
  \bottomrule
\end{tabular}
\end{NBAtable}

As can be seen, one player rises above all others in both PAR and VORP. That player is Nikola Jokic of the Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP season was. Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was doing it from the center position. Having a center that has the ability to perform in all aspects of the game, even those that his position does not require, proves his value to his team, which is why his value is so much higher in both the new PAR metric, and the accepted VORP metric. This logic applies to Nikola Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well. While they might not be considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, that can do anything on the court, and thus they are rewarded with a high PAR value. This makes sense, as without these players, a lot of the statistics their team accumulates are gone, so while they may not have as much value in the grand scheme of the NBA, they were very much the most valuable players for their teams. Another key thing to note is that some players, such as LeBron James, have a lower PAR than expected, and this could be due to the fact that they played most frequently in a position that did not match their skill set. LeBron James played primarily as a point guard, but his skillset matches that of a small forward or power forward. Thus, his strengths are not adequately measured, as he is essentially being played "out of position".
\begin{PGtable}[tbp]

  \caption{PAR Values from all Point Guards)
  \label{tab:PGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Luka Doncic & Dallas Mavericks & 4.61\\
  \midrule
 2 & Damian Lillard & Portland Trail Blazers & 4.47\\
  \midrule
 3 & Stephen Curry & Golden State Warriors & 4.17\\
  \midrule
 4 & Russell Westbrook & Washington Wizards & 4.05\\
  \midrule
 5 & Trae Young & Atlanta Hawks & 2.69\\
  \midrule
 6 & De'Aaron Fox & Sacramento Kings & 1.94\\
  \midrule
 7 & Chris Paul & Phoenix Suns & 1.93\\
  \midrule
 8 & Kyrie Irving & Brooklyn Nets & 1.74\\
  \midrule
 9 & Dejounte Murray & San Antonio Spurs & 1.64\\
  \midrule
 10 & Ja Morant & Memphis Grizzlies & 1.45\\
  \bottomrule
\end{tabular}
\end{PGtable}

\begin{SGtable}[tbp]
  \caption{PAR Values from all Shooting Guards)
  \label{tab:SGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Bradley Beal & Washington Wizards & 3.17\\
  \midrule
 2 & Devin Booker & Phoenix Suns & 2.74\\
  \midrule
 3 & Terry Rozier & Charlotte Hornets & 2.59\\
  \midrule
 4 & Zach Lavine & Chicago Bulls & 2.29\\
  \midrule
 5 & RJ Barrett & New York Knicks & 2.28\\
  \midrule
 6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
  \midrule
 7 & Jaylen Brown & Boston Celtics & 1.87\\
  \midrule
 8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
  \midrule
 9 & Buddy Hield & Sacramento Kings & 1.72\\
  \midrule
 10 & Norman Powell & Toronto Raptors & 1.37\\
  \bottomrule
\end{tabular}
\end{SGtable}

\begin{SFtable}[tbp]
  \caption{PAR Values from all Small Forwards)
  \label{tab:SFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Jayson Tatum & Boston Celtics & 3.96\\
  \midrule
 2 & Khris Middleton & Milwaukee Bucks & 2.39\\
  \midrule
 3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
  \midrule
 4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
  \midrule
 5 & Paul George & Los Angeles Clippers & 1.44\\
  \midrule
 6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
  \midrule
 7 & Jimmy Butler & Miami Heat & 1.41\\
  \midrule
 8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
  \midrule
 9 & Mikal Bridges & Phoenix Suns & 1.19\\
  \midrule
 10 & Jerami Grant & Detroit Pistons & 1.14\\
  \bottomrule
\end{tabular}
\end{SFtable}

\begin{PFtable}[tbp]
  \caption{PAR Values from all Power Forwards)
  \label{tab:PFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Julius Randle & New York Knicks & 6.49\\
  \midrule
 2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
  \midrule
 3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
  \midrule
 4 & Zion Williamson & New Orleans Pelicans & 3.07\\
  \midrule
 5 & Andrew Wiggins & Golden State Warriors & 2.26\\
  \midrule
 6 & Demar Derozan & San Antonio Spurs & 1.88\\
  \midrule
 7 & Tobias Harris & Philadelphia 76ers & 1.87\\
  \midrule
 8 & Pascal Siakam & Toronto Raptors & 1.72\\
  \midrule
 9 & John Collins & Atlanta Hawks & 1.35\\
  \midrule
 10 & Harrison Barnes & Sacramento Kings & 1.11\\
  \bottomrule
\end{tabular}
\end{PFtable}

\begin{Ctable}[tbp]
  \caption{PAR Values from all Centers)
  \label{tab:Ctable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Nikola Jokic & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & Orlando Magic & 6.55\\
  \midrule
 3 & Rudy Gobert & Utah Jazz & 3.10\\
  \midrule
 4 & Bam Adebayo & Miami Heat & 2.78\\
  \midrule
 5 & Joel Embiid & Philadelphia 76ers & 2.26\\
  \midrule
 6 & Clint Capela & Atlanta Hawks & 2.25\\
  \midrule
 7 & DeAndre Ayton & Phoenix Suns & 2.11\\
  \midrule
 8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
  \midrule
 9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
  \midrule
 10 & Kelly Olynyk & Miami Heat & 1.39\\
  \bottomrule
\end{tabular}
\end{Ctable}

@@

\section{Discussion}
% Analyzing entire study, show how you can use PAR now, did it achieve the overall goal I was looking for?
% Talk about drawbacks, what could be improved, etc.
Ultimately, the goal of this statistic is to allow a reader to gague a player's value to his team based on a league average player. As previously stated, the metric is adjusted so that a league average player has a PAR value of 0. Based on all other players' PAR values, we can create a sort of "legend", a rough guideline for what a player's role will be based on the threshold his PAR value falls under.

\bibliographystyle{chicago}
%\bibliography{citations.bib}
% \section*{acknowledgements}
The authors thank the University of Connecticut and the UConn Department of Statistics.

@@

% The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
% If there is more than one student author, you must move the comment below.
\section*{about the student author}
Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.

% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{press summary}

>>>>

\usepackage{amsmath, enumerate, quoting, subfigure, amssymb, url}

@@

\usepackage{xr}
%\externaldocument{isgee}
%\externaldocument{supp}

@@

\usepackage{geometry}
\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}

\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
\captionsetup{labelformat=simple, labelsep=period}
\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
\renewcommand{\theequation}{\arabic{equation}}
\makeatletter
\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
\makeatother
\setlength{\intextsep}{10pt}
\setlength{\abovecaptionskip}{2pt}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.90}

@@

% Abstracts are required.
\section*{Abstract}
In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other 
reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above 
Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player 
with one who is league average. The goal of this paper is to create a similar statistic, called Points Above 
Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team 
gains or loses by missing a certain player, and thus having to replace him with one who is "league 
average". The statistic is standardized and adjusted by both position and value to a player's given team. 
The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense 
and defense, as well as a positional and team adjustment. A comparison with the created metric along with 
other well-known advanced player metrics is done via a multiple regression.

% Keywords are required.
\section*{Keywords} 
NBA; Basketball; Player Performance; Basketball Metrics;
\vspace{.12 in}
% Start the main part of the manuscript here.
% Comment out section headings if inappropriate to your discipline.
% If you add additional section or subsection headings, use an asterisk * to avoid numbering.

@@

\section{Data}
% Include basic graphics here?
All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference 
website. Each teams total points throughout the course of the season were also collected from the 
Basketball Reference website. From the basic statistics, 4 metrics were created in order to calculate PAR. 
Offensive Points is a function of how many points a player will create on offense. While the coefficients vary 
by position, the statistics used are effective field goal percentage, three point percentage, free throw 
percentage, offensive rebounds, assists, points, and turnovers. Similarly, Defensive Points is a function of 
how many points a player helps prevent while his team is on defense. The coefficients also vary by position, 
but this metric is based on defensive rebounds, total rebounds, steals, blocks, and personal fouls. The 
Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is 
based on how many minutes a player plays relative to their team, as well as how many points they score 
relative to their teams total points. The last statistic created is Points Per Win, which is based on the 
average amount of points a player will create in a game. This function is based on the sum of Offensive and 
Defensive Points, and is scaled to incorporate the total number of games, minutes, and players in a season. 
This statistic is very similarly calculated to Runs Per Win in the WAR statistic. Given that over the course of 
a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in 
terms of strength of schedule. Advanced statistics for each player were also collected in order to perform a 
regression, to see how PAR compares with known and accepted metrics. Value Over Replacement Player, 
also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus 
Minus, also known as BPM. These statistics also help give a relative estimate of a player's value compared 
to that of an average player, but they translate the statistic to a league average team as well. PAR does not 
do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire 
league. If a player switched teams, his PAR value would most likely change, as his importance to one team 
may be more or less than it would to another. For simplicity, the team that a player played his most games 
on was taken into consideration for this metric. Other statistics used include Player Efficiency Rating, a 
per-minute 
rating of player performance, and Win Shares, which estimates the number of wins a player creates 
for his team throughout the season. Due to all of these metrics' relative similarity to PAR, it is suggested 
that if they are highly correlated with PAR, it is a successful metric. However, we expect some differentiation 
between the metrics, as they all vary slightly in what they attempt to convey. The relative correlation 
between all these statistics shows that PAR is related to other advanced metrics analyzing player efficiency, 
but also that it introduces something new in basketball statistics.

@@

\section{Results}
% Multiple Regression
% Analyze Graphs of PAR, filter by position perhaps?
% Any other tests that should be done?
First, the top 10 players in terms of PAR in the league will be analyzed. Then, the top 10 PAR values at each position will be evaluated.

\begin{table}[tbp]
  \caption{PAR Values from the Entire NBA}
  \label{tab:NBAtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Position & Team & PAR\\
  \midrule
 1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
  \midrule
 3 & Julius Randle & PF & New York Knicks & 6.49\\
  \midrule
 4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
  \midrule
 5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
  \midrule
 6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
  \midrule
 7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
  \midrule
 8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
  \midrule
 9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
  \midrule
 10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
  \bottomrule
\end{tabular}
\end{table}

As can be seen, one player rises above all others in both PAR and VORP. That player is Nikola Jokic of the 
Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP 
season was. Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was 
doing it from the center position. Having a center that has the ability to perform in all aspects of the game, 
even those that his position does not require, proves his value to his team, which is why his value is so 
much higher in both the new PAR metric, and the accepted VORP metric. This logic applies to Nikola 
Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well. While they might not be 
considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, 
that can do anything on the court, and thus they are rewarded with a high PAR value. This makes sense, as 
without these players, a lot of the statistics their team accumulates are gone, so while they may not have as 
much value in the grand scheme of the NBA, they were very much the most valuable players for their 
teams. Another key thing to note is that some players, such as LeBron James, have a lower PAR than 
expected, and this could be due to the fact that they played most frequently in a position that did not match 
their skill set. LeBron James played primarily as a point guard, but his skillset matches that of a small 
forward or power forward. Thus, his strengths are not adequately measured, as he is essentially being 
played "out of position".

\begin{table}[tbp]
  \caption{PAR Values from all Point Guards}
  \label{tab:PGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Luka Doncic & Dallas Mavericks & 4.61\\
  \midrule
 2 & Damian Lillard & Portland Trail Blazers & 4.47\\
  \midrule
 3 & Stephen Curry & Golden State Warriors & 4.17\\
  \midrule
 4 & Russell Westbrook & Washington Wizards & 4.05\\
  \midrule
 5 & Trae Young & Atlanta Hawks & 2.69\\
  \midrule
 6 & De'Aaron Fox & Sacramento Kings & 1.94\\
  \midrule
 7 & Chris Paul & Phoenix Suns & 1.93\\
  \midrule
 8 & Kyrie Irving & Brooklyn Nets & 1.74\\
  \midrule
 9 & Dejounte Murray & San Antonio Spurs & 1.64\\
  \midrule
 10 & Ja Morant & Memphis Grizzlies & 1.45\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Shooting Guards}
  \label{tab:SGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Bradley Beal & Washington Wizards & 3.17\\
  \midrule
 2 & Devin Booker & Phoenix Suns & 2.74\\
  \midrule
 3 & Terry Rozier & Charlotte Hornets & 2.59\\
  \midrule
 4 & Zach Lavine & Chicago Bulls & 2.29\\
  \midrule
 5 & RJ Barrett & New York Knicks & 2.28\\
  \midrule
 6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
  \midrule
 7 & Jaylen Brown & Boston Celtics & 1.87\\
  \midrule
 8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
  \midrule
 9 & Buddy Hield & Sacramento Kings & 1.72\\
  \midrule
 10 & Norman Powell & Toronto Raptors & 1.37\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Small Forwards}
  \label{tab:SFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Jayson Tatum & Boston Celtics & 3.96\\
  \midrule
 2 & Khris Middleton & Milwaukee Bucks & 2.39\\
  \midrule
 3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
  \midrule
 4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
  \midrule
 5 & Paul George & Los Angeles Clippers & 1.44\\
  \midrule
 6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
  \midrule
 7 & Jimmy Butler & Miami Heat & 1.41\\
  \midrule
 8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
  \midrule
 9 & Mikal Bridges & Phoenix Suns & 1.19\\
  \midrule
 10 & Jerami Grant & Detroit Pistons & 1.14\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Power Forwards}
  \label{tab:PFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Julius Randle & New York Knicks & 6.49\\
  \midrule
 2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
  \midrule
 3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
  \midrule
 4 & Zion Williamson & New Orleans Pelicans & 3.07\\
  \midrule
 5 & Andrew Wiggins & Golden State Warriors & 2.26\\
  \midrule
 6 & Demar Derozan & San Antonio Spurs & 1.88\\
  \midrule
 7 & Tobias Harris & Philadelphia 76ers & 1.87\\
  \midrule
 8 & Pascal Siakam & Toronto Raptors & 1.72\\
  \midrule
 9 & John Collins & Atlanta Hawks & 1.35\\
  \midrule
 10 & Harrison Barnes & Sacramento Kings & 1.11\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Centers}
  \label{tab:Ctable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Nikola Jokic & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & Orlando Magic & 6.55\\
  \midrule
 3 & Rudy Gobert & Utah Jazz & 3.10\\
  \midrule
 4 & Bam Adebayo & Miami Heat & 2.78\\
  \midrule
 5 & Joel Embiid & Philadelphia 76ers & 2.26\\
  \midrule
 6 & Clint Capela & Atlanta Hawks & 2.25\\
  \midrule
 7 & DeAndre Ayton & Phoenix Suns & 2.11\\
  \midrule
 8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
  \midrule
 9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
  \midrule
 10 & Kelly Olynyk & Miami Heat & 1.39\\
  \bottomrule
\end{tabular}
\end{table}

@@

\section{Discussion}
% Analyzing entire study, show how you can use PAR now, did it achieve the overall goal I was looking for?
% Talk about drawbacks, what could be improved, etc.
% Talk about how it is in agreement with existing measures
Ultimately, the goal of this statistic is to allow a reader to gauge a player's value to his team based on a 
league average player. As previously stated, the metric is adjusted so that a league average player has a 
PAR value of 0. Based on all other players' PAR values, we can create a sort of "legend", a rough guideline 
for what a player's role will be based on the threshold his PAR value falls under.

\bibliographystyle{chicago}
\bibliography{citations.bib}
\section*{Acknowledgements}
The authors thank the University of Connecticut and the UConn Department of Statistics.

@@

% The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
% If there is more than one student author, you must move the comment below.
\section*{About the Student Author}
Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.

% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{Press Summary}
